---
title: "Corporate Exploration"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    logo: ohridska5.jpg
    self_contained: no
---

```{r setup, include=FALSE}
library(flexdashboard)
```

<style>                     
  .navbar {
    background-color:red;
    border-color:black;
  }

.navbar-inverse .navbar-nav>.active>a, .navbar-inverse .navbar-nav>.active>a:hover, .navbar-inverse .navbar-nav>.active>a:focus {
  color: black;
  background-color: #feb0b0;
}

.navbar-inverse .navbar-nav > li > a:hover, .navbar-inverse .navbar-nav > li > a:focus {
  background-color: #feb0b0
}

</style>           


```{r}
#Libraries

library(data.table)
library(dplyr)
library(lubridate)
library(DT)
library(crosstalk)
library(plotly)
```


Corporate Data {data-orientation=rows data-icon="ion-ios-home"}
=====================================  

```{r}
#Libraries

library(data.table)
library(dplyr)
library(lubridate)
library(crosstalk)
```

```{r}
#Load data
setwd("~/directory_3/database_tables")

corporate_clients <- fread("./corporate_profile.csv", drop = "V1")

```
`

### Date of data extract

``` {r}
valueBox("07/06/2017", icon = "glyphicon-calendar", color="rgb(100,100,100)")

```

###  Number of corporate clients

```{r}
n <- nrow(corporate_clients)

valueBox(n, icon = "glyphicon-user", color="#64c864")
```

###  Number of variables

```{r}
n <- nrow(corporate_clients)

valueBox("42", icon = "glyphicon-list-alt", color="#0099ff")
```

Corporate Stats {data-orientation=rows data-icon="Row glyphicon-stats"}
=====================================  

The scope of clients we analyze is with the following legal structure: 

-  ДООЕЛ (Limited Liability Company of One Person)
-  ДОО (Limited Liability Company)
-  Јавно Трговско Друштво (Corporation - Inc) 
-  Јавно претпријатие (State Owned)

Row
-------------------------------------
```{r}
corporate_clients <- filter(corporate_clients, organization_structure == "ДООЕЛ" | organization_structure == "Друштво со ограничена одговорност" | organization_structure == "Јавно трговско друштво" | organization_structure == "Јавно претпријатие")
```

### Firm Size

```{r}
library(highcharter)

firm_size <- as.data.frame(table(corporate_clients$firm_size))

colnames(firm_size)[1] <- "col_label"
colnames(firm_size)[2] <- "size"


hchart(firm_size, "pie", hcaes(x = col_label, label=size,y = size)) %>%
hc_plotOptions(pie =list(dataLabels = list(enabled = TRUE,format="{point.percentage:.2f} %"))) %>%
  
hc_tooltip(pointFormat = "
Nominal value: {point.y:,.0f}<br>")

```


### Location

```{r}
location_nominal <- as.data.frame(table(corporate_clients$post_city))
location_percent <- as.data.frame(prop.table(table(corporate_clients$post_city)))

colnames(location_nominal)[1] <- "Location"
colnames(location_nominal)[2] <- "Nominal"

colnames(location_percent)[1] <- "Location"
colnames(location_percent)[2] <- "Freq_percent"

location_percent$Freq_percent <- round(location_percent$Freq_percent, digits = 2)
location_percent$Freq_percent <- location_percent$Freq_percent * 100

location <- merge(location_nominal, location_percent, by = "Location", all.x = TRUE)

location_n <- arrange(location, desc(Freq_percent))
location_n <- head(location_n, n = 10)
location_n <- arrange(location_n, desc(Freq_percent))

location_n$colorr <- "#ffb347"

hchart(location_n, "bar", hcaes(x = Location, label=Location,y = Freq_percent, color=colorr)) %>%

hc_tooltip(pointFormat = "
Percent: {point.y:,.0f}<br>")
```

Row
-------------------------------------

### Seniority 

```{r}

corporate_profile <- corporate_clients

corporate_profile$REGDATUM <- ymd(corporate_profile$REGDATUM)

corporate_profile$foundation_year <- year(corporate_profile$REGDATUM)  

corporate_profile <- mutate(corporate_profile, seniority_years =
                              2017 - foundation_year)

seniority <- as.data.frame(table(corporate_profile$seniority_years))
seniority <- seniority[c(-1, -38), ]

seniority$Freq <- as.numeric(seniority$Freq)

seniority <- mutate(seniority, percent = Freq/sum(Freq))
seniority <- mutate(seniority, percent = round(percent, digits = 2))
seniority <- mutate(seniority, percent = percent * 100)

colnames(seniority)[1] <- "seniority_years"
colnames(seniority)[2] <- "nominal"
colnames(seniority)[3] <- "percent"

t <- ggplot(seniority)  +
   geom_point(aes(as.factor(seniority_years), 
                  nominal), 
             size = 2, 
             color="magenta") +
  geom_line(aes(as.factor(seniority_years), 
                nominal,
                group = 1, alpha = 0.5), 
            color = "magenta") +

  xlab("") + 
  ylab("") +
  theme(legend.title = element_blank()) +
  theme_minimal()

ggplotly(t) 
```

Row
-------------------------------------

### 

```{r}
opis <- as.data.frame(table(corporate_clients$OPIS.x))

opis
```



Products {data-orientation=rows data-icon="ion-ios-home"}
=====================================  

Transactions {data-orientation=rows data-icon="ion-ios-home"}
=====================================  